%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Mechatronics Engineer - NeMo (NewMobility) Robotics} % Job title
    {Uber} % Organization
    {San Francisco, CA} % Location
    {August 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Oversaw a JDM project with a Taiwanese hardware CRM to produce an Android based 360 degree camera system mounted on a micromobility scooter from Concept to Production.}
        \item {Handled cross-functional QA on EE design, hardware/mechanical change requests.}
        \item {Mentored junior team members and aided them in owning design projects and establishing priorities.}
        \item {Created an assembly cell to facilitate final assembly of hardware units with overhead torque controlled fastener drivers and automated labeling and barcode scan based asset/QA tracking.}
        \item {Identified the need for a hardware tracking database and created an Airtable Base along with a suite of client side software in python and LabVIEW that automatically tracked production gates, firmware/software updates, QA inspections } 
        \item {Owned a power and digital interface PCB to serve as an electrical bridge between vehicle and camera. Wrote all firmware in C for the MCU.} 
        \item {Designed a 5 discreet antenna solution for Wifi MIMO, GPS, LTE MIMO that was housed in a micromobility scooter.}
        \item {Designed a cellular modem solution for a high speed Cat-4 LTE connection on a micromobility vehicle with simplified compliance, time-to-market, and speed as primary design criteria.}
        \item {Owned mech. design of IP68 sealing system with 3 discreet electronics enclosure chambers and 6 electrical passthroughs.}
        \item {Successfully served as interim team EM of a 5 person mechatronics group during month-long absence of EM.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer - LiDAR Sensors and Deployments} % Job title
    {Ouster Inc.} % Organization
    {San Francisco, CA} % Location
    {June 2019 - August 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{https://www.fleetguide.io/}
                {Worked on FleetGuide, a LiDAR based sensor suite for trucks to provide drivers with better spatial awereness. \color{darkblue}Link.}}
        \item {Solved design issues with deployed sensor systems on fleets of trucks, ranging from water ingress to creating fault handling/reaction
        systems on ruggedized truck mounted Linux boxes.}
        \item {Wrote automated provisioning and test code for fleet of ruggedized Linux based LiDAR systems mounted to garbage trucks.}
        \item {Conducted data analysis for fleet health monitoring to aid in scaling up fleet using the ELK stack, Big Query and Tableou.}
      \end{cvitems}
    }

  \cventry
    {Founder} % Job title
    {Stocker Freight} % Organization
    {New York, NY} % Location
    {2017 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{https://paulsammut.com/lib/exe/fetch.php/seed_deck_r14.pdf}
              {Raised seed round and founded Stocker, dedicated to creating an autonomous freight service for cities. \color{darkblue}Link.}}
        \item {\href{https://paulsammut.com/doku.php/primo_robot}
            {Built a tech-demo street robot name Primo using ROS capable of operating autonomously in the street. \color{darkblue}Link.}}
        \item {\href{https://paulsammut.com/doku.php/stereo_cameras}
            {Integrated RTAB-Map appearance based SLAM to create PCL maps and localize within them. \color{darkblue}Link.}}
        \item {\href{http://bit.ly/2T3d4sU}
            {Wrote ROS code integrating stereo cams, mono cams, IMU, and wheel encoders to provide odometry fused with an EKF. \color{darkblue}Link.}}
        \item {Created a simulation environment with fully defined URDF and custom sim nodes for HIL and SIL testing in Gazebo}
      \end{cvitems}
    }

  \cventry
    {Robotics Engineer} % Job title
    {Robotics Consulting | Rockefeller University} % Organization
    {New York, NY} % Location
    {2016 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {\href{https://paulsammut.com/doku.php/robodolf}
            {Acquired and managed a robotics contract to create an autonomous catamaran for dolphin vocalization research. \color{darkblue}Link.}}
        \item {Integrated IMU, GPS, Cameras, Motor Controllers, Long Range RF Telemetry and Control, 
                    LiFePo4 Battery System, and wrote Mission Control software for autonomous operation.}
        \item {\href{http://bit.ly/2BSBD1c}{Created a publisher-subscribers
            software framework using the Actor Framework allowing for node-like processes. \color{darkblue}Link.}}
      \end{cvitems}
    }

  \cventry
    {Founder} % Job title
    {Ramos Alarm Clock | Sammut Tech LLC} % Organization
    {Hoboken, NJ} % Location
    {2012 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{http://bit.ly/2NvLgHA}{Invented a novel alarm clock that forced users out of bed by use of a remote keypad. Took idea from concept to prototype to shipped hardware product. \color{darkblue}Link.}}
        \item {Created a successful Kickstarter and pre-order campaign raising \$250K in pre-orders and successfully shipped a consumer electronics hardware product.}
        \item {Setup a factory in New Jersey, managed 2 engineers and labor hires to manufacture product.}
        \item {Managed capital acquisitions, supply chain, manufacturing plans, inventory forecast schedules, and product strategy.}
      \end{cvitems}
    }

  \cventry
    {Senior Research Engineer} % Job title
    {Davidson Lab | Stevens Institute of Technology} % Organization
    {Hoboken, NJ} % Location
    {2009 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed new high-perfomance technology projects from the specification phase to testing and validation.} 
        \item {Conducted fundamental physics research on High Speed Supercavitating Vehicles (underwater rockets).}
        \item {Designed thousands of mechanical parts and assemblies in CAD for fabrication utilizing numerous materials, in complex tolerence stackups in electromechcanical and pneumatic and subsea applications.}
        \item {Created instrumentation and control apparatus utilizing various sensors, pneumatic systems, still and video photography systems interfaced to separate RTOS and standard computers on a custom distributed network.} 
        \item {Operated, maintained, and upgraded a fleet of UUVs operating in the Hudson River.}
        \item {Created HIL testing apparatus utilizing mathematical models to validate system performance.} 
        \item {Designed electronic wiring systems for power, analog and digital comms and connector solutions.}
        \item {Wrote and supported mission critical launch control software for rocket systems.} 
        \item {Designed and managed the creation of a rocket control surface subsystem with humming bird level dynamic response.}
      \end{cvitems}
    }

%  \cventry
%    {Field Engineering Intern} % Job title
%    {East Side Access | Judlau Contracting, Inc.} % Organization
%    {Queens, NY} % Location
%    {2008 - 2009} % Date(s)
%    {%
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Worked on a team executing a \$10B subway construction project in
%            NY - oversaw the construction of Sump Pump Chamber \#7.}
%      \end{cvitems}
%    }

  \cventry
    {Machine Shop Apprentice} % Job title
    {Institute Machine Shop | Stevens Institute of Technology} % Organization
    {Hoboken, NJ} % Location
    {2007 - 2009} % Date(s)
    {%
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Machined parts based on provided drawings and learned fundamental concepts of Design For Manufacture.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
